---
title: "Weight of Fish"
author: "sierra lander"
date: "`summer 2024"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}

if(!require("Bolstad")) {install.packages("Bolstad");require("Bolstad")}
```


## Perch


### Best Models

```{r}
perchmodel = lm(Weight~ ., data=Perch)
summary.lm(perchmodel)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```



The best two regressor model to predict weight is Height and Width 

### Best Two regressor model

```{r}
Perch2=lm(Weight~Height+Width,data=Perch)
summary.lm(Perch2)
```

## Pike

### Best Models

```{r}
pikemodel = lm(Weight~ ., data=Pike)
summary.lm(pikemodel)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```



### Best Two regressor model


```{r}
Pike2=lm(Weight~Length1+Length3,data=Pike)
summary.lm(Pike2)
```


The best model was length1 and length3

## Roach

### Best Models


```{r}
roachmodel = lm(Weight~ ., data=Roach)
summary.lm(roachmodel)
```


```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```



### Best Two regressor model


```{r}
roach2=lm(Weight~Length3+Width,data=Roach)
summary.lm(roach2)
```

The best regressor model was Length3 and Width


## Final Summary Statements


The best regressor model for Pike was  length1 and length3

The best regressor model for Perch was Height and Width 

The best regressor model for roach was  Length3 and Width





